---
title: "Basic_vidualization Practice R"
excerpt: "Data analysis is a process of inspecting, cleansing, transforming and modeling data with the goal of discovering useful information, informing conclusions and supporting decision-making. Data analysis has multiple facets and approaches, encompassing diverse techniques under a variety of names, and is used in different business, science, and social science domains. In today's business world, data analysis plays a role in making decisions more scientific and helping businesses operate more effectively"
categories: [Data analysis]
author: "Jin"
date: "10/01/2020"
use_math: true
comments: true
tag: [R, Data analysis, kaggle]
output:
  md_document:
    variant: markdown_github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## First R Markdown with movie rating data

* Read data

```{r movies}
movies <- read.csv('data/Movie Ratings.csv',header=T)
```

```{r summary}
summary(movies)
```

##  * change the column names

```{r colnames}
colnames(movies) <- c('name','genre','criticsratings','audienceratings','budgetmillions','releaseyear')
```

## To see the types of genre
```{r}
levels(movies$genre)
head(movies)
```

## changing the numeric column to categorical
```{r}
movies$releaseyear<-as.factor(movies$releaseyear)
levels(movies$releaseyear)
```

## ggplot2 package
```{r echo=FALSE}
library(ggplot2)
ggplot(data=movies,aes(x=criticsratings,y=audienceratings)) + geom_point()
```

## color and size setting 

```{r echo=FALSE}
r<-ggplot(data=movies,aes(x=criticsratings,y=audienceratings))+geom_point(color='red',size=3)
r
```

## Color and Size mapping

```{r echo=FALSE}
r+geom_point(aes(color='yellow'))
r+geom_point(aes(size=budgetmillions))
```

## changing the graph type

```{r  echo=FALSE}
ggplot(data=movies,aes(x=budgetmillions))+
  geom_histogram(binwidth=10,color='blue',fill='green')
```

## genre mappig

```{r ,echo=FALSE}
ggplot(data=movies,aes(x=budgetmillions))+
  geom_histogram(binwidth=10,color='black',aes(fill=genre))
```


## Using facet grid to divide the graph according to genre
```{r ,echo=FALSE}
ggplot(data=movies,aes(x=criticsratings,y=audienceratings))+geom_point(color='red',size=3)+
  facet_grid(.~genre)
```


```{r  echo=FALSE}
d <- ggplot(data=movies,aes(x=budgetmillions))+
  geom_density(color='black',stack=10,aes(fill=genre))
d
```

## Adding new layer for limiting the yscale
```{r  echo=FALSE}
ggplot(data=movies,aes(x=budgetmillions))+
  geom_histogram(binwidth=10,color='black',aes(fill=genre))+
  coord_cartesian(ylim=c(0,50))
```

## histograms with facet grid
```{r  echo=FALSE}
ggplot(data=movies,aes(x=budgetmillions))+
  geom_histogram(binwidth=10,color='black',aes(fill=genre))+
  facet_grid(genre~.,scales='free')
```

## Scaling x and y coordinates
```{r  echo=FALSE}
t <- ggplot(data=movies,aes(x=criticsratings,y=audienceratings,color=genre))+geom_point(size=3)+
  facet_grid(genre~releaseyear)+xlim(0,100)+ylim(0,50)
t
```

## adding themes to plots
```{r  echo=FALSE}
library(ggthemes)
```
## see the difference between d & d + theme_economist()
```{r  echo=FALSE}
d + theme_economist()
```



















